Import OLIS spectral data

### 2023-12-07 Code/OlisImportPurCalc.Rmd
Fixed saveRDS filepath so that PUR generated data is saved.
Changed path to DataOut

DataOut <- file.path("..", "ProcessedData")

@@

 save nested 
```{r Save rds and csv}

saveRDS(object = PicoNestedPurOlisData, file = file.path(DataOut, "PicoNestedPurOlisData.Rds"))

# write_csv(PicoNestedPurOlisData, file = file.path(DataOut, paste(Project, "NestedPurOlisData",".csv",sep = ""),fsep = .Platform$file.sep))

>>>>

DataOut <- file.path("..", "Data", "ProcessedData","MultiCultiEmissionData")

@@

# save nested 
```{r Save rds}

# saveRDS(object = PicoNestedPurOlisData, file = file.path(DataOut, "PicoNestedPurOlisData.Rds"))

saveRDS(PicoNestedPurOlisData, file.path(DataOut, paste(Project, "PicoNestedPurOlisData.Rds", sep = "_"), fsep = .Platform$file.sep))
